\chapter{Notes on future chapters}

\begin{description}

\item[Unary notation]
depends on successor

\item[Binary notation]
depends on Unary notation

\item[abstraction]
an explanation of why a number is an abstraction. related to the abstraction `green' for example. the set of all green things?
depends on howmany

\item[ordinal and cardinal]
to be added:
if a line of sheep are going through a gate, and we count each sheep, does the number `5' refer to the fifth sheep or the first five sheep?
(digression about the origins of counting in outsourcing of shepherding)

\item[after ordinals and cardinals]
\begin{itemize}
\item
There are uses of numbers which do not fall into either category. The purpose of car number plates is not to tell us how many cars there are (although it gives us some idea), nor is it to establish which order cars were registered in (although again it gives us some idea). Number plates along with serial numbers, credit card numbers, and so on are a very simple use of numbers which are only used to distinguish between distinct things. Neither of the special properties of numbers that we have discussed here matter.
\item
On the other hand some \fterm{measurements}, for example of length, can involve both properties of number. A battleship which is 40 metres long is (notionally) made up of 40 sections each a meter long, and thus the `how many' type of counting is involved. On the other hand the sections have a precise order, and we can refer to a place on the ship by saying which of the numbered sections it belongs to.
\end{itemize}

\item[orderings]
discussing the common features of the ordering `greater than' and the ordering `subset of'. 
\item[sequences]
a sequence is a set with a total ordering.
followed by \ldots
\item[strings]
and 
\item[trees]

\item[mappings]

\item[Finiteness]

\item[Countability]
\item[Uncountability]

\item[Huffman encoding]
\item[Conway's numbers]

\item[slide rule]
\item[well-tempering]

\item[Breadth first search, depth first search]
\item[Lex and co-lex] 

\item[Affine calculations]

\item[The Farey tree]

\item[There is no completely honest way to make infinity dollars]

\item[The length of a potato]


\end{description}


